### 2017-05-18 paper/documents/0.abstract.tex
Add files via upload

\begin{abstract}

This is abstract\cite{eggert2015classification}

\end{abstract}

### 2017-05-18 paper/documents/4.experiment.tex
Add files via upload

\section{EXPERIMENTS}
\label{sec:exp}
This is experiment

\subsection{Dataset}
\label{sec:dataset}

This is dataset

\subsection{Results and Discussion}
\label{subsec:results}

This is results and discussion

### 2017-05-18 paper/documents/5.conclusion.tex
Add files via upload

\section{CONCLUSION}
\label{sec:conclusion}

This is conclusion

### 2017-05-18 codes/draft_code.R
- add reduced classes based on Gao - cite no.5

@@ -21,52 +21,73 @@ disabler = c(88,14,33)
 # loadItems <- data.frame(read.csv("heroes.csv", header = T, sep = ","))
 
 # get all match id from TI 2014 - 2016
-#TI2014 = read.csv("TI2014.csv", header = T, sep = ",")
-#TI2015 = read.csv("TI2015.csv", header = T, sep = ",")
-TI2016 = read.csv("TI2016.csv", header = T, sep = ",")
-#KIEV = read.csv("KIEVMAJOR.csv", header = T, sep = ",")
-MANILA = read.csv("MANILAMAJOR.csv", header = T, sep = ",")
-SHANGHAI = read.csv("SHANGHAIMAJOR.csv", header = T, sep = ",")
-BOSTON = read.csv("BOSTONMAJOR.csv", header = T, sep = ",")
+# TI2014 = read.csv("TI2014.csv", header = T, sep = ",")
+# TI2015 = read.csv("TI2015.csv", header = T, sep = ",")
+# TI2016 = read.csv("TI2016.csv", header = T, sep = ",")
+# KIEV = read.csv("KIEVMAJOR.csv", header = T, sep = ",")
+# MANILA = read.csv("MANILAMAJOR.csv", header = T, sep = ",")
+# SHANGHAI = read.csv("SHANGHAIMAJOR.csv", header = T, sep = ",")
+# BOSTON = read.csv("BOSTONMAJOR.csv", header = T, sep = ",")
 # merge the data
-matchesData <- rbind(TI2016, MANILA, SHANGHAI, BOSTON)
-# matchesData <- read.csv("TI2016.csv", header = T, sep = ",")
+# matchesData <- rbind(MANILA, SHANGHAI, BOSTON)
+ matchesData <- read.csv("TI2016.csv", header = T, sep = ",")
 
 # the data consist 10 match id in one match because 10 player have own macth id
 matchesId <- unique(matchesData$match_id)
-# x = get_match_details(3143516306)
+# x = get_match_details(3188810567)
+# x$players$
 # dataset format 
-# accountid ,level, kill, death, assist , neutral kill, GPM, XPM, last hit, denied, Hero damaged, hero healing, tower damage,tower kill, gold, XP, hero as class
+# accountid ,level, kda, kill, death, assist , neutral kill, obs, sen, GPM, XPM, last hit, denied, Hero damaged, hero healing, tower damage,tower kill, gold, XP, hero as class
 for ( i in matchesId )
 {
[…]

### 2017-05-19 codes/data_normalization.R
+ add data normalization code and their results

@@ -1,0 +1,124 @@
+# Citation: Singh, Bikesh Kumar, Kesari Verma, and A. S. Thoke. "Investigations on impact of feature normalization techniques on classifier's performance in breast tumor classification." International Journal of Computer Applications 116.19 (2015).
+
+########################################################################################
+# This technique normalizes data in range [0, 1].
+# linear scaling to [0,1]
+Linear.Scaling.function <- function(x)
+{
+  return ((x-min(x))/(max(x)-min(x)))
+}
+
+Linear.Scaling.Normalization <- function(x)
+{
+  as.data.frame(lapply(x, Linear.Scaling.function))
+}
+
+Min.Max.function <- function(x)
+{
+  min_new = -1;
+  max_new = 1;
+  return (((x-min(x))/(max(x)-min(x)))*(max_new-min_new)+min_new)
+}
+
+Min.Max.Normalization <- function(x)
+{
+  as.data.frame(lapply(x, Min.Max.function))
+}
+
+
+########################################################################################
+# This functions transformation technique to normalize data in range [-1, 1].or they called standard normalization
+#z score standarization (single column)
+Z.Score <- function(x) 
+{
+  return ((x - mean(x) ) / sd(x))
+}
+
+Z.Score.Normalization <- function(x) 
+{
+  as.data.frame(lapply(x, Z.Score))
+}
+
+#z score standarization using base package (Multi columns)
+Z.Score.Default.Normalization <- function(x){
+  
+  as.data.frame(scale(x))
+}
+
+
+
+########################################################################################
+# Non linear normalization
+# techniques may be used in cases where data are not evenly
+# distributed around the mean.
+# This function is based on nonlinear (i.e., exponential, logarithmic, sigmoid etc.) 
+# function normalize data in range [0, 1].
+Softmax.Scaling <- function(x)
+{
+  return (1/(1+(exp(-(x)))))
+  
+}
+
+Softmax.Scaling.Normalization <- function(x)
+{
+  as.data.frame(lapply(x, Softmax.Scaling))
+}
+
+
+##############################
+#############################################################################
+# READ DATA
+#############################################################################
+# Path File
+SetPathFile = "trainingdata.csv";
+
+
+# -------------------------------------------------------
+# Read Data and separate from class column
[…]

### 2017-05-20 paper/documents/1.introduction.tex
- change manuscript structure

\section{Introduction}

This is Introduction also the related work.

### 2017-05-20 paper/documents/2.background.tex
- change manuscript structure

\section{Background}
\label{sec:background}

This is related work

### 2017-05-22 paper/documents/0.abstract.tex
- update paper

@@
 
-This is abstract\cite{eggert2015classification}
+Multi-player online battle arena games are the most successful games.
+Every players have own specific roles in this team based game.
+Dota2 is the most popular for this games.
+This paper analyzing player roles and their behavior using supervised machine learning and also investigates the applicability of feature normalization to enhance accuracy of prediction result.We provide an in-depth discussion and novel approaches for constructing complex attributes from low-level data extracted from replay files.
+Using attribute evaluation techniques, we are able to reduce a larger set of candidate attributes down to a manageable number.
+Random Forest is the most stable and best performing classifier in our results.
 

### 2017-05-22 paper/documents/1.introduction.tex
- update paper

@@
 
-This is Introduction also the related work.
+Computer games is a big business.
+competitive gaming growing the interest in this business.
+The competitive gaming events, the so-called electronic sports (sPorts).
+Multi-player online batle arena (MOBA) games are the most popular and succesful games in this regard.
+Game tournaments always give significant awards with big prize of money.
+Mostly, professional player can make a living from the prize.
+\\
+In this paper we analyzing the player roles using supervised machine learning (ML) , investigate the applicability of feature normalization to enhance accuracy of prediction results.
+We also comparing our result with previous paper.
+Christoph Eggert on his paper said that their most stable and performing classifier is logistic regression.
+We will use the same classification method with their work.
+The different is we will using ROpenDota to built the data set.

### 2017-05-22 paper/documents/2.background.tex
- update paper

@@
 
-This is related work
+Dota2 is team based game in Multi-player Online Battle Arena (MOBA).
+Each team have five players.
+Every player will choose their hero in pre-match games.
+Currently, there is 113 heroes, 166 current items.
+Dota2 game design is separated the heroes with three types.
+The first is agility heroes type, the second is strength heroes type and the last is intelligent heroes type.
+Every heroes have own specialty and weakness.
+The items can be combine into upgrade-able item which is will give more status in heroes abilities.
+\\

### 2017-05-22 paper/documents/1.introduction.tex
- update paper

@@
 The different is we will using ROpenDota to built the data set.
+\\
+This paper contributes to the state of the art in several ways: We provide an in-depth discussion and novel approaches regarding the construction of complex attributes from low level data extracted from Dota 2 replay files, together with an evaluation of these attributes with respect to different classifiers.
+Based on the resulting reduced set of attributes, we compare and discuss the performance of a range of supervised classification algorithms, including logistic regression, random forest decision trees, support vector machines (in combination with Sequential Minimal Optimization), naive Bayes and Bayesian networks, classifying both with a newly established larger set of player roles, as well as with a reduced set inspired by related work ~\cite{eggert2015classification}.

### 2017-05-22 paper/documents/2.background.tex
- update paper

@@
 \\
+Hero selection is important aspect of the game.
+Team needs to balance the heroes with different abilities that able to fulfill certain of roles and strategies.
+In the beginning of the game, each player will get 650 gold to buy starting items.
+\\
+Dota2 map layout split into three lanes. Each lanes has three defensive towers.

### 2017-05-28 paper/documents/2.background.tex
- update paper

@@
 Dota2 is team based game in Multi-player Online Battle Arena (MOBA).
+It is divided by two areas, the Dire and the Radiant.
 Each team have five players.
@@
 \\
-Dota2 map layout split into three lanes. Each lanes has three defensive towers.
+Dota2 map layout split into three lanes.
+Each lanes has three defensive towers.
+the Dire lanes and the Radiant lanes are quite different.
+the top of Radiant it is called off-lane , meanwhile in Dire, the top lane is called safe-lane.
+The bottom lane of Radiant is called safe-lane, while in Dire it is called off-lane.
+And the middle lane will remain same.
+\\

### 2017-06-01 paper/documents/4.experiment.tex
- change manuscript structure
- update paper

@@
-\section{EXPERIMENTS}
+\section{Experiments}
 \label{sec:exp}
-This is experiment
 
-\subsection{Dataset}
-\label{sec:dataset}
+\subsection{Data Collection}
+\label{sec:datacollection}
 
-This is dataset
+We are using ROpenDota by Rosdyana Kusuma to built our data set.
+ROpenDota is an API wrapper service for OpenDota in R.
+We labeling players from replay and the replay based on The International 2016 and Kiev Major, which contains 8419 labeled players.
+Using replay data from professional players will guarantee our data set from low level data.
 
-\subsection{Results and Discussion}
-\label{subsec:results}
+\subsection{Attribute Construction and Evaluation}
+\label{sec:attconsandeval}
+Attributes for evaluation is presented in table 1.
 
-This is results and discussion
+\subsection{Space and Movement}
+\label{spaceandmovement}
+Most of player roles depend on the lane (see figure x) which is the most active in the early game.

### 2017-06-02 paper/documents/1.introduction.tex
- update paper

@@
 Computer games is a big business.
-competitive gaming growing the interest in this business.
+Competitive gaming growing the interest in this business.
 The competitive gaming events, the so-called electronic sports (sPorts).
-Multi-player online batle arena (MOBA) games are the most popular and succesful games in this regard.
+State-of-the-art multi-player online batle arena (MOBA) games are the most popular and succesful games in this regard.
 Game tournaments always give significant awards with big prize of money.
 Mostly, professional player can make a living from the prize.
-\\
+
 In this paper we analyzing the player roles using supervised machine learning (ML) , investigate the applicability of feature normalization to enhance accuracy of prediction results.
@@
 The different is we will using ROpenDota to built the data set.
-\\
+
+An approach to ML in computer games in general was proposed by Drachen et al.\cite{drachen2014skill} .
+They suggest using unsupervised learning algorithms, specifically k-means and \textit{Simplex Volume Maximization}, to cluster player behavior data.
+
+Our investigation about applicability and performance of \textit{supervised machine learning} (ML) to classify player roles based on behavior in Dota 2, the most popular MOBA game.
+
 This paper contributes to the state of the art in several ways: We provide an in-depth discussion and novel approaches regarding the construction of complex attributes from low level data extracted from Dota 2 replay files, together with an evaluation of these attributes with respect to different classifiers.

### 2017-06-02 paper/documents/2.background.tex
- update paper

@@
 
-Dota2 is team based game in Multi-player Online Battle Arena (MOBA).
+\textit{Dota 2} is team based game in Multi-player Online Battle Arena (MOBA).
 It is divided by two areas, the Dire and the Radiant.
@@
 The items can be combine into upgrade-able item which is will give more status in heroes abilities.
-\\
+
 Hero selection is important aspect of the game.
@@
 In the beginning of the game, each player will get 650 gold to buy starting items.
-\\
-Dota2 map layout split into three lanes.
+
+Dota 2 map layout split into three lanes.
 Each lanes has three defensive towers.
@@
 And the middle lane will remain same.
-\\
+
+\subsection{Player Roles}
+\label{sec:player_roles}
+
+Player roles or play styles is the way how player will choose and try to act as their roles or styles in the games.
+It is important to note that these roles describe a different facet of play than classic player type classifications (e.g.
+after battle

### 2017-06-03 paper/documents/0.abstract.tex
- update paper

--- 2017-05-18 paper/documents/0.abstract.tex
@@
 
-This is abstract\cite{eggert2015classification}
+The state of the art, computer games are big business, which is also reflected in the growing interest in competitive gaming.
+\textit{Multi-player online battle arena} games are the most successful games.
+Every players have own specific roles in this team based game.
+\textit{Dota 2} is the most popular for this games.
+This paper analyzing player roles and their behavior using \textit{supervised machine learning} and also investigates the applicability of feature normalization to enhance accuracy of prediction result.We provide an in-depth discussion and novel approaches for constructing complex attributes from low-level data extracted from replay files.
+Using attribute evaluation techniques, we are able to reduce a larger set of candidate attributes down to a manageable number.
+\textit{Random Forest} the decision trees algorithm is the most stable and best performing classifier in our results.
 

### 2017-06-03 paper/documents/1.introduction.tex
- update paper

@@
 
-Our investigation about applicability and performance of \textit{supervised machine learning} (ML) to classify player roles based on behavior in Dota 2, the most popular MOBA game.
+Our investigation about applicability and performance of \textit{supervised machine learning} (ML) to classify player roles based on behavior in \textit{Dota 2}, the most popular MOBA game.
+Such information could be useful for game designer to better understand how their game design influences emergent gameplay and player behavior but also for players, both casual and professional, who want to analyze their own performance or who want to learn from the others.
+It could also support casters and moderators in commentating and presenting matches.
+Furthermore, this research might hold implications for social and other research concerned with (human behavior in) games.
+While ML has been applied to games and traditional sports, most works are either interested in questions like spatial behavior, trying to predict the match outcome, or otherwise trying to correlate performance to certain events or behaviors.
+In contrast, we aim at building a classifier that is largely independent of individual players performance and that is also not tied to the overall match outcome but that is able to identify a player's role in term of the non-formally defined roles established as common grounds within the \textit{Dota 2} or MOBA community.
 

### 2017-06-03 paper/documents/2.background.tex
- update paper

@@
 
-\textit{Dota 2} is team based game in Multi-player Online Battle Arena (MOBA).
-It is divided by two areas, the Dire and the Radiant.
+\textit{Dota 2} is team based game in \textit{Multi-player Online Battle Arena} (MOBA).
+It is divided by two areas, the \textit{Dire} and the \textit{Radiant}.
 Each team have five players.
@@
 Currently, there is 113 heroes, 166 current items.
-Dota2 game design is separated the heroes with three types.
+\textit{Dota 2} game design is separated the heroes with three types.
 The first is agility heroes type, the second is strength heroes type and the last is intelligent heroes type.
@@
 
-Dota 2 map layout split into three lanes.
+\textit{Dota 2} map layout split into three lanes.
 Each lanes has three defensive towers.

### 2017-06-03 paper/documents/4.experiment.tex
- update paper

@@
 Attributes for evaluation is presented in table 1.
+While some attributes correspond directly to summary data, attributes that capture positional information the fighting behavior require more complex processing of the replay data.
+Different attribute filters implemented in the Java library WEKA \cite{hall2009weka} to determine the best set of attributes.
+Our results with the \textit{WtrapperSubsetEval} class with best-first search are presented in table 1.
+We have chosen this algorithm for our nal attribute selection because it resulted in the highest accuracy with our labeled data set.
+For classification we selected all attributes that were present in at least four folds, excluding assists, as this resulted in the overall highest accuracy.
+In the following sections we describe the algorithms and heuristics we developed to calculate the attributes that cannot be directly obtained from replay files.
+They can be grouped into ve rough categories: space and movement, early ganks, team fights, support items, and damage types.
+Not all of the attributes we describe in this section were finally chosen to be used for classification within this work but they might prove valuable for future works.
 
@@
 Most of player roles depend on the lane (see figure x) which is the most active in the early game.
+Player lane information also provides the constructor for the other attributes, e.g., the \textit{lane partners}.

### 2017-06-05 paper/documents/0.abstract.tex
- using 12pt font size

@@
 The state of the art, computer games are big business, which is also reflected in the growing interest in competitive gaming.
-\textit{Multi-player online battle arena} games are the most successful games.
+\textit{Multi-player online battle arena} games are the most successful competitive gaming in computer games industry.
 Every players have own specific roles in this team based game.
@@
 \textit{Random Forest} the decision trees algorithm is the most stable and best performing classifier in our results.
+Again, \textit{Random Forest} although not the best performing classifier  but it is proved to be very stable and well suited to this domain.
 

### 2017-06-05 paper/documents/2.background.tex
- update paper

@@
 It is important to note that these roles describe a different facet of play than classic player type classifications (e.g.
-after battle
+after Bartle \cite{bartle1996hearts}) which aim to classify expressed character traits of the players and were designed to match role-play style games.
+Comparison of videos, Online guides, and commentary of professional players and commentators are our sources for selection and characterization of the player roles.
+Player roles definitions and naming conventions will in any case differ slightly among the player base and shift over time as the game evolves, constituting another challenge for \textit{Machine Learning} applications in this area.
+We isolated five player roles for the main \textit{Machine Learning} task, which strike a balance between covering common play styles in great detail while leaving out some exotic styles which are rarely observed or are minor variations of the other styles.
+The isolated roles were: \textit{Carry} - who are usually weak and need protection early on, but are very strong in later stages, often deciding games.
+Carry typically end up with a high amount of last hits, gold per minute and overall kills, but they can get them in quite different ways.

### 2017-06-05 paper/documents/4.experiment.tex
- update paper

@@
 Our results with the \textit{WtrapperSubsetEval} class with best-first search are presented in table 1.
-We have chosen this algorithm for our nal attribute selection because it resulted in the highest accuracy with our labeled data set.
+We have chosen this algorithm for our final attribute selection because it resulted in the highest accuracy with our labeled data set.
 For classification we selected all attributes that were present in at least four folds, excluding assists, as this resulted in the overall highest accuracy.
 In the following sections we describe the algorithms and heuristics we developed to calculate the attributes that cannot be directly obtained from replay files.
-They can be grouped into ve rough categories: space and movement, early ganks, team fights, support items, and damage types.
+They can be grouped into five rough categories: space and movement, early ganks, team fights, support items, and damage types.
 Not all of the attributes we describe in this section were finally chosen to be used for classification within this work but they might prove valuable for future works.
@@
 \label{spaceandmovement}
-Most of player roles depend on the lane (see figure x) which is the most active in the early game.
+% figures
+\begin{figure}
+\centering
+\includegraphics[width=2.5in]{./figures/lane_map.png}
+\caption{\textit{Dota 2} map designed with three lane. Top lane, middle lane and also bottom lane.}
+\label{fig:map_lane}
+\end{figure}
+
+Most of player roles depend on the lane (see figure \ref{fig:map_lane}) which is the most active in the early game.
 Player lane information also provides the constructor for the other attributes, e.g., the \textit{lane partners}.

### 2017-06-05 paper/documents/4.experiment.tex
- update paper

@@
 \label{sec:attconsandeval}
-Attributes for evaluation is presented in table 1.
+Attributes for evaluation is presented in table \ref{table:table1}.
 While some attributes correspond directly to summary data, attributes that capture positional information the fighting behavior require more complex processing of the replay data.
 Different attribute filters implemented in the Java library WEKA \cite{hall2009weka} to determine the best set of attributes.
-Our results with the \textit{WtrapperSubsetEval} class with best-first search are presented in table 1.
+Our results with the \textit{WrapperSubsetEval} class with best-first search are presented in table 1.
 We have chosen this algorithm for our final attribute selection because it resulted in the highest accuracy with our labeled data set.
@@
 \label{spaceandmovement}
-% figures
+
 \begin{figure}
@@
 Player lane information also provides the constructor for the other attributes, e.g., the \textit{lane partners}.
+In the early game, players commonly have three main positions: \textit{top lane}, \textit{mid lane}, or \textit{bottom lane}.
+In additional, the \textit{jungle} areas also can be used ( see figure \ref{fig:map_jungle}).
+Or, players can have a \textit{roaming} position, it means that they will move around the map instead of focusing in specific lane.
+
+\begin{figure}
+\centering
+\includegraphics[width=2.5in]{./figures/map_jungle.png}
+\caption{\textit{Dota 2} map jungle areas divided into two areas, \textit{Dire} and \textit{Radiant} jungle.}
+\label{fig:map_jungle}
+\end{figure}
+
+\begin{table}[]
+\centering
+\begin{tabular}{|l|c|}
+\hline
+\rowcolor[HTML]{BBDAFF} 
+\multicolumn{1}{|c|}{\cellcolor[HTML]{BBDAFF}\textbf{Attribute}} & \textbf{Number of Folds} \\ \hline
+KDA Ratio* = (Kills + Assists) / (Deaths + 1)                    & 10                       \\ \hline
+\rowcolor[HTML]{FFFFC7} 
+Last Hits*                                                       & 10                       \\ \hline
+Early Ganks*+                                                    & 10                       \\ \hline
+\rowcolor[HTML]{FFFFC7} 
+Number of Support Items*+                                        & 10                       \\ \hline
+Damage to Neutral Creeps*+                                       & 10                       \\ \hline
+\rowcolor[HTML]{FFFFC7} 
+Damage to Regular Creeps*+                                       & 10                       \\ \hline
+Lane Partners*+                                                  & 10                       \\ \hline
+\rowcolor[HTML]{FFFFC7} 
+Kills*                                                           & 9                        \\ \hline
+Experience*                                                      & 5                        \\ \hline
+\rowcolor[HTML]{FFFFC7} 
+Deaths*                                                          & 5                        \\ \hline
+Assists                                                          & 5                        \\ \hline
+\rowcolor[HTML]{FFFFC7} 
+Team Fight Participation*+                                       & 4                        \\ \hline
+Early Movement (Visited Cells)*+                                 & 4                        \\ \hline
+\rowcolor[HTML]{FFFFC7} 
+Damage to Heroes*+                                               & 4                        \\ \hline
+Solo Lane+                                                       & 2                        \\ \hline
+\rowcolor[HTML]{FFFFC7} 
+Damage to Towers+                                                & 1                        \\ \hline
+Chosen Hero                                                      & 0                        \\ \hline
+\rowcolor[HTML]{FFFFC7} 
+Gold                                                             & 0                        \\ \hline
+\end{tabular}
+\caption{Attributes evaluated for classification. Attributes marked with + are not directly
+available from replays. Attributes marked with {*} were finally selected for classification.
+Number of Folds shows in how many folds an attribute was selected by WEKA’s
+WrapperSubsetEval class using 10-fold cross-validation for each classification.}
+\label{table:table1}
+\end{table}

### 2017-06-05 paper/documents/4.experiment.tex
* caption in table using small caps, according to IEEE should be all caps, but looks ugly

@@
 
+\renewcommand{\arraystretch}{1.5}
+\setlength{\tabcolsep}{12pt}
 \begin{table}[]
+\caption{Attributes evaluated for classification.
+Attributes marked with + are not directly available from replays.
+Attributes marked with {*} were finally selected for classification.
+Number of Folds shows in how many folds an attribute was selected by WEKA’s WrapperSubsetEval class using 10-fold cross-validation for each classification.}
+\label{table:table1}
 \centering
-\begin{tabular}{|l|c|}
+\begin{tabular}{|c|c|}
 \hline
-\rowcolor[HTML]{BBDAFF} 
-\multicolumn{1}{|c|}{\cellcolor[HTML]{BBDAFF}\textbf{Attribute}} & \textbf{Number of Folds} \\ \hline
+\textbf{Attribute}                            & \textbf{Number of Folds} \\ \hline
 KDA Ratio* = (Kills + Assists) / (Deaths + 1) & 10                       \\ \hline
-\rowcolor[HTML]{FFFFC7} 
 Last Hits*                                    & 10                       \\ \hline
 Early Ganks*+                                 & 10                       \\ \hline
-\rowcolor[HTML]{FFFFC7} 
 Number of Support Items*+                     & 10                       \\ \hline
 Damage to Neutral Creeps*+                    & 10                       \\ \hline
-\rowcolor[HTML]{FFFFC7} 
 Damage to Regular Creeps*+                    & 10                       \\ \hline
 Lane Partners*+                               & 10                       \\ \hline
-\rowcolor[HTML]{FFFFC7} 
 Kills*                                        & 9                        \\ \hline
 Experience*                                   & 5                        \\ \hline
-\rowcolor[HTML]{FFFFC7} 
 Deaths*                                       & 5                        \\ \hline
 Assists                                       & 5                        \\ \hline
-\rowcolor[HTML]{FFFFC7} 
 Team Fight Participation*+                    & 4                        \\ \hline
 Early Movement (Visited Cells)*+              & 4                        \\ \hline
-\rowcolor[HTML]{FFFFC7} 
 Damage to Heroes*+                            & 4                        \\ \hline
 Solo Lane+                                    & 2                        \\ \hline
-\rowcolor[HTML]{FFFFC7} 
 Damage to Towers+                             & 1                        \\ \hline
 Chosen Hero                                   & 0                        \\ \hline
-\rowcolor[HTML]{FFFFC7} 
 Gold                                          & 0                        \\ \hline
 \end{tabular}
-\caption{Attributes evaluated for classification. Attributes marked with + are not directly
-available from replays. Attributes marked with {*} were finally selected for classification.
-Number of Folds shows in how many folds an attribute was selected by WEKA’s
-WrapperSubsetEval class using 10-fold cross-validation for each classification.}
-\label{table:table1}
 \end{table}

### 2017-06-05 paper/documents/2.background.tex
- update paper

@@
 \textit{Dota 2} map layout split into three lanes.
-Each lanes has three defensive towers.
+Each lanes has three defensive towers (see figure \ref{fig:map_lane}).
 the Dire lanes and the Radiant lanes are quite different.
@@
 Carry typically end up with a high amount of last hits, gold per minute and overall kills, but they can get them in quite different ways.
+\textit{Mid Laner} - this kind of playing style mostly will get middle lane position since early game.
+focusing on collecting more gold to obtain high percentage lane of gold in early ten minutes.
+\textit{Offlaner} - safe lane as their common lane.
+\textit{Dire} jungle is safe lane for dire team, otherwise the \textit{Radiant} jungle is safe lane for radiant team.
+Usually have balance between \textit{networth} and efficiently lane gold in early ten minutes.
+\textit{Roaming Support} - support heroes mostly weak, roaming support will have roaming attribute from replay file, this player roles will buy support item such as: \textit{Observer ward} and \textit{Sentry ward} for vision.
+\textit{Hard Support} - sometimes called babysitter, because this playing style need to do everything for supporting the Carry.
+Mostly, buy support items much more than roaming support.

### 2017-06-05 paper/documents/4.experiment.tex
- update paper

@@
 \label{sec:attconsandeval}
+
 Attributes for evaluation is presented in table \ref{table:table1}.
@@
 
-\subsection{Space and Movement}
-\label{spaceandmovement}
-
 \begin{figure}
 \centering
-\includegraphics[width=2.5in]{./figures/lane_map.png}
+\includegraphics[width=1.5in]{./figures/lane_map.png}
 \caption{\textit{Dota 2} map designed with three lane. Top lane, middle lane and also bottom lane.}
@@
 
-Most of player roles depend on the lane (see figure \ref{fig:map_lane}) which is the most active in the early game.
+\textbf{Player Lane} Most of player roles depend on the lane (see figure \ref{fig:map_lane}) which is the most active in the early game.
 Player lane information also provides the constructor for the other attributes, e.g., the \textit{lane partners}.
@@
 \centering
-\includegraphics[width=2.5in]{./figures/map_jungle.png}
+\includegraphics[width=1.5in]{./figures/map_jungle.png}
 \caption{\textit{Dota 2} map jungle areas divided into two areas, \textit{Dire} and \textit{Radiant} jungle.}
@@
 \end{table}
+
+\textbf{Lane Partners and Solo Lane} To calculate the lane attribute from lane partners and solo lane can be determine by comparing the number of players.
+Player in \textit{jungle} position or \textit{roaming} are always assigned with zero lane partners, while players who is sharing the other lane, such as top, mid or bottom lane are corresponding with number of their \textit{teammates} in the current lane.
+Solo lane attribute included in our attributes as an alternative to the lane partners.
+The value of this attribute will be true if a player is assigned to one of the tree main lanes without any teammate and otherwise false.
+
+\textbf{Support Items} Player who considering playing as support mostly must buy support items.
+Many items in \textit{Dota 2} are useful for support player.
+List of common suppor items: \textit{Courier}, \textit{Flying Courier}, \textit{Observer Ward} and \textit{Sentry Ward}.
+
+\textbf{Damage Types} We categorized damage type based on player roles and requirement of other attributes: damage to tower, damage to heroes, damage to regular creeps, damage to neutral creeps and damage to ancient creeps.
+
+\subsection{Feature Normalization}
+\label{sec:featurenorm}
+
+We applied feature normalization on this paper in order to enhance high accuracy.

### 2017-06-06 paper/documents/4.experiment.tex
- update paper

@@
 
-We applied feature normalization on this paper in order to enhance high accuracy.
+An approach of \textit{Feature Normalization} to enhance the accuracy result proved by Singh \cite{singh2015investigations}.
+We applied feature normalization on this paper to cross check if this methodology can help to tweak accuracy of classification results.
+Various normalization techniques in this study are:
+
+\textbf{Z-Score Normalization}, A very common techniques to normalize the feature to zero mean and unit variance is Z-score normalization \cite{jayalakshmi2011statistical}.
+It is a linear technique which initially mean ( \(\bar{x}\) ) and standard deviation ( \(\sigma\) ) of the specific feature values are computed using:
+
+\begin{equation}
+\bar{x}=\frac{1}{N}\sum_{i-1}^{N}x_{i}
+\end{equation}
+
+and,
+\begin{equation}
+\sigma^2=\frac{1}{N-1}\sum_{i-1}^{N}(x_{i}-\bar{x})^2
+\end{equation}
+
+the normalized feature is then given by:
+\begin{equation}
+\bar{x}_i=\frac{x_i-\bar{x}}{\sigma}
+\end{equation}
+
+\textbf{Min-Max Normalization}, This technique performs a linear transformation on the original data.
+For mapping a value, of an attribute \(x_i\) from range [min(\(x_i\)), max(\(x_i\))] to a new range [min \(x_new,\),max \(x_new\), the normalized feature is given by:
+
+\begin{equation}
+\hat{x}_i=\frac{X_i-min(x_i)}{max(x_i)-min(x_i)}
+\end{equation}
+
+The advantage of Min-Max normalization is that it preserves the relationship among the original data values \cite{manikandan2013achieving}.
+In this study \(max\,x_{new}=1\) and \(min\,x_{new}=-1\) is used.
+
+\textbf{Linar Scaling to Unit Range}, This is also a linear transformation technique to normalize data in range[0,1].
+Given a lower bound min(\(x_i\)) and upper bound max(\(x_i\)) of an attribute \(x_i\), the normalized value is given by:
+
+\begin{equation}
+\hat{x}_i=\frac{x_i-min(x_i)}{max(x_i)-min(x_i)}
+\end{equation}
+
+Linear scaling to unit range is special case of min-max normalization in which max\(\,x_{new}\)=1 and min\(\,x_{new}\)=0.
+
+\textbf{Softmax Scaling}, In addition to linear scaling, non linear normalization techniques may be used in cases where data are not evenly distributed around the mean \cite{theodoridis2010introduction}.
+In such cases the transformations based on nonlinear (i.e., exponential, logarithmic, sigmoid etc) functions can be used to map the data within specified intervals.
+One such popular technique is so called softmax scaling which squashes the data value non linearly in the interval [0,1].
+the normalized feature is given by;
+
+\begin{equation}
+\hat{x}_i=\frac{1}{1+e^{-y}}
+\end{equation}
+
+where \(y=\frac{x_i-\bar{x}}{r\sigma}\) and \textit{r} is a user defined parameter.
+in the above equation that for small values of y i.e., for values of \(x_i\) closer to mean, y is an approximately linear function.
+Values away from mean are squashed exponentially.

### 2017-06-06 paper/documents/5.conclusion.tex
- update paper

@@
-\section{CONCLUSION}
+\section{Results and Conclusion}
 \label{sec:conclusion}
 
-This is conclusion
+\subsection{Result}
+\label{sec:results}
+
+We trained and evaluated several different classifier using 10-fold cross-validation and independent test on our data set.
+The classifiers was based on existing works and complemented by commonly used classification approaches.
+It included: \textit{Random forest decision trees}, \textit{logistic regression}, \textit{support vector machines with sequential minimal optimization}, \textit{naive bayes classifier}, and \textit{bayesian networks}.
+We are using WEKA library and tool for the technical platform.
+The classifiers were evaluated according to several established performance metric (accuracy, mean absolute error (MAE) \cite{willmott2005advantages}, and area under ROC (AUC) \cite{huang2005using}.
+
+\renewcommand{\arraystretch}{1.5}
+\setlength{\tabcolsep}{8pt}
+\begin{table}[]
+\centering
+\caption{Summary of 10-fold cross -validation and independent test accuracies with feature normalization data set.}
+\label{table:table2}
+\resizebox{0.5\textwidth}{!}{%
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+\multicolumn{1}{|c|}{\textbf{Full Classes}}    & \multicolumn{2}{c|}{\textbf{10-Folds Cross Validation}} & \multicolumn{2}{c|}{\textbf{Independent Test}} \\ \hline
+Original                                       & Random forest                 & 89.37\%                 & Random forest                & 88.54\%         \\ \hline
+Linear Scale                                   & Random forest                 & 89.77\%                 & Logistic Regression          & 81.65\%         \\ \hline
+Min-Max Normalization                          & Random forest                 & 89.53\%                 & Logistic Regression          & 81.65\%         \\ \hline
+Softmax Scaling                                & Random forest                 & 80.13\%                 & Random forest                & 79.81\%         \\ \hline
+Z-Score Normalization                          & Random forest                 & 89.68\%                 & Random forest                & 86.52\%         \\ \hline
+\multicolumn{1}{|c|}{\textbf{Reduced Classes}} & \multicolumn{2}{c|}{\textbf{10-Folds Cross Validation}} & \multicolumn{2}{c|}{\textbf{Independent Test}} \\ \hline
+Original                                       & Random forest                 & 94.52\%                 & Random forest                & 93.53\%         \\ \hline
+Linear Scale                                   & Random forest                 & 94.33\%                 & Random forest                & 88.48\%         \\ \hline
+Min-Max Normalization                          & Random forest                 & 94.39\%                 & Random forest                & 88.78\%         \\ \hline
+Softmax Scaling                                & Random forest                 & 92.59\%                 & Random forest                & 92.34\%         \\ \hline
+Z-Score Normalization                          & Random forest                 & 89.40\%                 & Random forest                & 92.10\%         \\ \hline
+\end{tabular}%
+}
+\end{table}
+
+Table \ref{table:table2} list the highest accuracy from 10-fold cross-validation and independent test of our works.
+Random forest is the most stable with good performance from our works.
+The accuracy result also reasonable.
+it means the good accuracy is not over fitting after checking the cross-validation with the independent test results.
+
+\renewcommand{\arraystretch}{1.5}
+\setlength{\tabcolsep}{8pt}
+\begin{table}[]
+\centering
+\caption{Comparison with previous works.}
+\label{table:table3}
+\resizebox{0.5\textwidth}{!}{%
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline
+\textbf{Classifier}             & \multicolumn{2}{c|}{\textbf{Accuracy}} & \multicolumn{2}{c|}{\textbf{Mean Absolute Error}} & \multicolumn{2}{c|}{\textbf{Wgt. Avg. AUC}} \\ \hline
+\textbf{Full set of classes}    & *                  & **                & *                       & **                      & *                    & **                   \\ \hline
+Random Forest                   & 76.27\%            & 89.37\%           & 0.0905                  & 0.0691                  & 0.943                & 0.984                \\ \hline
+Logistic Regression             & 75.85\%            & 82.64\%           & 0.0826                  & 0.1013                  & 0.947                & 0.962                \\ \hline
+SMO                             & 75.28\%            & 81.65\%           & 0.1753                  & 0.2503                  & 0.926                & 0.91                 \\ \hline
+Bayesian Networks               & 72.03\%            & 70.54\%           & 0.0801                  & 0.122                   & 0.933                & 0.927                \\ \hline
+Naive Bayes                     & 70.76\%            & 74.43\%           & 0.0769                  & 0.1055                  & 0.933                & 0.95                 \\ \hline
+\textbf{Reduced set of classes} & *                  & **                & *                       & **                      & *                    & **                   \\ \hline
+Bayesian Networks               & 96.58\%            & 92.61\%           & 0.0322                  & 0.0919                  & 0.995                & 0.973                \\ \hline
+SMO                             & 96.15\%            & 88.15\%           & 0.2308                  & 0.1185                  & 0.975                & 0.875                \\ \hline
+Logistic Regression             & 96.15\%            & 88.15\%           & 0.0381                  & 0.1662                  & 0.993                & 0.953                \\ \hline
+Naive Bayes                     & 95.58\%            & 89.84\%           & 0.0383                  & 0.2319                  & 0.994                & 0.89                 \\ \hline
+Random Forest                   & 91.17\%            & 94.52\%           & 0.1182                  & 0.0916                  & 0.985                & 0.987                \\ \hline
+\end{tabular}%
+}
+\end{table}
+
+Table \ref{table:table3}, comparison result of our works with previous works. Which is our works is quite better in full set classes. Random forest still dominating for the accuracy result.
+
+\subsection{Conclusion}
+\label{sec:conclusion}
+
+Not yet :v

### 2017-06-06 paper/documents/0.abstract.tex
- update paper
* fixed grammar

--- 2017-05-22 paper/documents/0.abstract.tex
@@
 
-Multi-player online battle arena games are the most successful games.
-Every players have own specific roles in this team based game.
-Dota2 is the most popular for this games.
-This paper analyzing player roles and their behavior using supervised machine learning and also investigates the applicability of feature normalization to enhance accuracy of prediction result.We provide an in-depth discussion and novel approaches for constructing complex attributes from low-level data extracted from replay files.
+State-of-the-art, Computer games are big business, which is also reflected in the growing interest in competitive gaming.
+\textit{Multi-player online battle arena} games are the most successful competitive gaming in computer games industry.
+Every player has own specific roles in this team based game.
+\textit{Dota 2} is the most popular for this games.
+This paper analyzing player roles and their behavior using \textit{supervised machine learning} and also investigates the applicability of feature normalization to enhance the accuracy of prediction result.We provide an in-depth discussion and novel approaches for constructing complex attributes from low-level data extracted from replay files.
 Using attribute evaluation techniques, we are able to reduce a larger set of candidate attributes down to a manageable number.
-Random Forest is the most stable and best performing classifier in our results.
+\textit{Random Forest} the decision trees algorithm is the most stable and best-performing classifier in our results.
+Again, \textit{Random Forest} although not the best performing classifier it is proved to be very stable and well suited to this domain.
 

### 2017-06-06 paper/documents/1.introduction.tex
- update paper
* fixed grammar

@@
 The competitive gaming events, the so-called electronic sports (sPorts).
-State-of-the-art multi-player online batle arena (MOBA) games are the most popular and succesful games in this regard.
-Game tournaments always give significant awards with big prize of money.
-Mostly, professional player can make a living from the prize.
+State-of-the-art, multi-player online battle arena (MOBA) games are the most popular and successful games in this regard.
+Game tournaments always give significant awards with the big prize of money.
+Mostly, the professional player can make a living from the prize.
 
-In this paper we analyzing the player roles using supervised machine learning (ML) , investigate the applicability of feature normalization to enhance accuracy of prediction results.
-We also comparing our result with previous paper.
-Christoph Eggert on his paper said that their most stable and performing classifier is logistic regression.
+In this paper we analyze the player roles using supervised machine learning (ML) , investigate the applicability of feature normalization to enhance the accuracy of prediction results.
+We also compare our result with previous paper.
+Christoph Eggert on his paper said that their most stable and performing classifier is the logistic regression.
 We will use the same classification method with their work.
-The different is we will using ROpenDota to built the data set.
+The different is we will using ROpenDota to build the data set.
 
-An approach to ML in computer games in general was proposed by Drachen et al.\cite{drachen2014skill} .
+An approach to ML in computer games, in general, was proposed by Drachen et al.\cite{drachen2014skill} .
 They suggest using unsupervised learning algorithms, specifically k-means and \textit{Simplex Volume Maximization}, to cluster player behavior data.
@@
 Our investigation about applicability and performance of \textit{supervised machine learning} (ML) to classify player roles based on behavior in \textit{Dota 2}, the most popular MOBA game.
-Such information could be useful for game designer to better understand how their game design influences emergent gameplay and player behavior but also for players, both casual and professional, who want to analyze their own performance or who want to learn from the others.
+Such information could be useful for the game designer to better understand how their game design influences emergent gameplay and player behavior but also for players, both casual and professional, who want to analyze their own performance or who want to learn from the others.
 It could also support casters and moderators in commentating and presenting matches.
@@
 While ML has been applied to games and traditional sports, most works are either interested in questions like spatial behavior, trying to predict the match outcome, or otherwise trying to correlate performance to certain events or behaviors.
-In contrast, we aim at building a classifier that is largely independent of individual players performance and that is also not tied to the overall match outcome but that is able to identify a player's role in term of the non-formally defined roles established as common grounds within the \textit{Dota 2} or MOBA community.
+In contrast, we aim at building a classifier that is largely independent of an individual players performance and that is also not tied to the overall match outcome but that is able to identify a player's role in term of the non-formally defined roles established as common grounds within the \textit{Dota 2} or MOBA community.
 
-This paper contributes to the state of the art in several ways: We provide an in-depth discussion and novel approaches regarding the construction of complex attributes from low level data extracted from Dota 2 replay files, together with an evaluation of these attributes with respect to different classifiers.
+This paper contributes to the state of the art in several ways: We provide an in-depth discussion and novel approaches regarding the construction of complex attributes from low-level data extracted from Dota 2 replay files, together with an evaluation of these attributes with respect to different classifiers.
 Based on the resulting reduced set of attributes, we compare and discuss the performance of a range of supervised classification algorithms, including logistic regression, random forest decision trees, support vector machines (in combination with Sequential Minimal Optimization), naive Bayes and Bayesian networks, classifying both with a newly established larger set of player roles, as well as with a reduced set inspired by related work ~\cite{eggert2015classification}.

### 2017-06-06 paper/documents/2.background.tex
* fixed grammar

--- 2017-06-05 paper/documents/2.background.tex
@@
 It is divided by two areas, the \textit{Dire} and the \textit{Radiant}.
-Each team have five players.
+Each team has five players.
 Every player will choose their hero in pre-match games.
 Currently, there is 113 heroes, 166 current items.
-\textit{Dota 2} game design is separated the heroes with three types.
+\textit{Dota 2} game design has separated the heroes with three types.
 The first is agility heroes type, the second is strength heroes type and the last is intelligent heroes type.
-Every heroes have own specialty and weakness.
-The items can be combine into upgrade-able item which is will give more status in heroes abilities.
+Every hero has own specialty and weakness.
+The items can be combined into a upgrade-able item which is will give more status in heroes abilities.
 
-Hero selection is important aspect of the game.
-Team needs to balance the heroes with different abilities that able to fulfill certain of roles and strategies.
+Hero selection is an important aspect of the game.
+The team needs to balance the heroes with different abilities that able to fulfill certain of roles and strategies.
 In the beginning of the game, each player will get 650 gold to buy starting items.
@@
 \textit{Dota 2} map layout split into three lanes.
-Each lanes has three defensive towers.
+Each lanes has three defensive towers (see figure \ref{fig:map_lane}).
 the Dire lanes and the Radiant lanes are quite different.
-the top of Radiant it is called off-lane , meanwhile in Dire, the top lane is called safe-lane.
+the top of Radiant it is called off-lane, meanwhile, in Dire, the top lane is called safe-lane.
 The bottom lane of Radiant is called safe-lane, while in Dire it is called off-lane.
@@
 
-Player roles or play styles is the way how player will choose and try to act as their roles or styles in the games.
+Player roles or play styles is the way how the player will choose and try to act as their roles or styles in the games.
 It is important to note that these roles describe a different facet of play than classic player type classifications (e.g.
@@
 Comparison of videos, Online guides, and commentary of professional players and commentators are our sources for selection and characterization of the player roles.
-Player roles definitions and naming conventions will in any case differ slightly among the player base and shift over time as the game evolves, constituting another challenge for \textit{Machine Learning} applications in this area.
+Player roles definitions and naming conventions will, in any case, differ slightly among the player base and shift over time as the game evolves, constituting another challenge for \textit{Machine Learning} applications in this area.
 We isolated five player roles for the main \textit{Machine Learning} task, which strike a balance between covering common play styles in great detail while leaving out some exotic styles which are rarely observed or are minor variations of the other styles.
-The isolated roles were: \textit{Carry} - who are usually weak and need protection early on, but are very strong in later stages, often deciding games.
+The isolated roles were: \textit{Carry} - who are usually weak and need protection early on but are very strong in later stages, often deciding games.
 Carry typically end up with a high amount of last hits, gold per minute and overall kills, but they can get them in quite different ways.
+\textit{Mid Laner} - this kind of playing style mostly will get middle lane position since early game.
+focusing on collecting more gold to obtain high percentage lane of gold in early ten minutes.
+\textit{Offlaner} - safe lane as their common lane.
+\textit{Dire} jungle is the safe lane for the Dire team, otherwise, the \textit{Radiant} jungle is the safe lane for the Radiant team.
+Usually, have a balance between \textit{networth} and efficiently lane gold in early ten minutes.
+\textit{Roaming Support} - support heroes mostly weak, roaming support will have roaming attribute from replay file, this player role will buy support item such as: \textit{Observer ward} and \textit{Sentry ward} for vision.
+\textit{Hard Support} - sometimes called the babysitter, because this playing style needs to do everything for supporting the Carry.
+Mostly, buy support items much more than roaming support.

### 2017-06-06 paper/documents/4.experiment.tex
* fixed grammar

@@
 We labeling players from replay and the replay based on The International 2016 and Kiev Major, which contains 8419 labeled players.
-Using replay data from professional players will guarantee our data set from low level data.
+Using replay data from professional players will guarantee our data set from low-level data.
 
@@
 We have chosen this algorithm for our final attribute selection because it resulted in the highest accuracy with our labeled data set.
-For classification we selected all attributes that were present in at least four folds, excluding assists, as this resulted in the overall highest accuracy.
-In the following sections we describe the algorithms and heuristics we developed to calculate the attributes that cannot be directly obtained from replay files.
+For classification, we selected all attributes that were present in at least four folds, excluding assists, as this resulted in the overall highest accuracy.
+In the following sections, we describe the algorithms and heuristics we developed to calculate the attributes that cannot be directly obtained from replay files.
 They can be grouped into five rough categories: space and movement, early ganks, team fights, support items, and damage types.
@@
 
-\textbf{Player Lane} Most of player roles depend on the lane (see figure \ref{fig:map_lane}) which is the most active in the early game.
+\textbf{Player Lane} Most of the player roles depend on the lane (see figure \ref{fig:map_lane}) which is the most active in the early game.
 Player lane information also provides the constructor for the other attributes, e.g., the \textit{lane partners}.
@@
 In additional, the \textit{jungle} areas also can be used ( see figure \ref{fig:map_jungle}).
-Or, players can have a \textit{roaming} position, it means that they will move around the map instead of focusing in specific lane.
+Or, players can have a \textit{roaming} position, it means that they will move around the map instead of focusing in a specific lane.
 
@@
 
-\textbf{Lane Partners and Solo Lane} To calculate the lane attribute from lane partners and solo lane can be determine by comparing the number of players.
-Player in \textit{jungle} position or \textit{roaming} are always assigned with zero lane partners, while players who is sharing the other lane, such as top, mid or bottom lane are corresponding with number of their \textit{teammates} in the current lane.
+\textbf{Lane Partners and Solo Lane} To calculate the lane attribute from lane partners and solo lane can be determined by comparing the number of players.
+The player in \textit{jungle} position or \textit{roaming} are always assigned with zero lane partners, while players who are sharing the other lane, such as top, mid or bottom lane are corresponding with a number of their \textit{teammates} in the current lane.
 Solo lane attribute included in our attributes as an alternative to the lane partners.
@@
 
-\textbf{Damage Types} We categorized damage type based on player roles and requirement of other attributes: damage to tower, damage to heroes, damage to regular creeps, damage to neutral creeps and damage to ancient creeps.
+\textbf{Damage Types} We categorized damage type based on player roles and requirement of other attributes: damage to the tower, damage to heroes, damage to regular creeps, damage to neutral creeps and damage to ancient creeps.
 
@@
 
-\textbf{Softmax Scaling}, In addition to linear scaling, non linear normalization techniques may be used in cases where data are not evenly distributed around the mean \cite{theodoridis2010introduction}.
-In such cases the transformations based on nonlinear (i.e., exponential, logarithmic, sigmoid etc) functions can be used to map the data within specified intervals.
+\textbf{Softmax Scaling}, In addition to linear scaling, nonlinear normalization techniques may be used in cases where data are not evenly distributed around the mean \cite{theodoridis2010introduction}.
+In such cases, the transformations based on nonlinear (i.e., exponential, logarithmic, sigmoid etc) functions can be used to map the data within specified intervals.
 One such popular technique is so called softmax scaling which squashes the data value non linearly in the interval [0,1].
-the normalized feature is given by;
+the normalized feature is given by:
 

### 2017-06-06 paper/documents/5.conclusion.tex
* fixed grammar

@@
 
-We trained and evaluated several different classifier using 10-fold cross-validation and independent test on our data set.
-The classifiers was based on existing works and complemented by commonly used classification approaches.
+We trained and evaluated several different classifiers using 10-fold cross-validation and independent test on our data set.
+The classifiers were based on existing works and complemented by commonly used classification approaches.
 It included: \textit{Random forest decision trees}, \textit{logistic regression}, \textit{support vector machines with sequential minimal optimization}, \textit{naive bayes classifier}, and \textit{bayesian networks}.
@@
 The accuracy result also reasonable.
-it means the good accuracy is not over fitting after checking the cross-validation with the independent test results.
+it means the good accuracy is not overfitting after checking the cross-validation with the independent test results.
 
@@
 
-Table \ref{table:table3}, comparison result of our works with previous works. Which is our works is quite better in full set classes. Random forest still dominating for the accuracy result.
+Table \ref{table:table3}, the comparison result of our works with previous works. Which is our works is quite better in full set classes. Random forest still dominating for the accuracy result.
+
+Classify the player roles is not easy.
+We asking \textit{Dota 2} experts to manually classify the player roles.
+The responses were highly divergent among them.
+This illustrates that the classification tasks is difficult, even for human experts.
+Our data set from the professional tournament (
 

### 2017-06-07 paper/documents/5.conclusion.tex
- update paper

@@
 This illustrates that the classification tasks is difficult, even for human experts.
-Our data set from the professional tournament (
+Our data set from the professional tournament (Kiev Major 2017 and \textit{The International 2016}) with 8419 data set, We separated into 70\% for training data and 30\% the rest for testing data.
+We also classified our data set with the same attributes but with a reduced set of classes (\textit{carry}, \textit{support}) inspired by Gao et al.
+\cite{gao2013classifying}, classification with our attributes achieved a higher accuracy for our data set.
+A direct comparison is not possible since the data sets differ.
+Still, the result indicate that classification with a reduced set of classes works well and could already be employed for many applications.
+Summarizing, we can state that the full set of classes shows promising results but also highlights that, although these classes are accepted by \textit{Dota 2} experts, some are ambiguous even to humans manually labeling the data.
 
-\subsection{Conclusion}
+\subsection{Conclusion and Future Work}
 \label{sec:conclusion}

### 2017-06-07 paper/documents/5.conclusion.tex
- beta release

@@
 \centering
-\caption{Comparison with previous works.}
+\caption{Comparison with previous works. Value with (*) is the previous work results, and marked by (**) is our work results.}
 \label{table:table3}
@@
 
-Not yet :v
+In this paper, we presented and discussed an approach to apply machine learning techniques for the classification of player roles in \textit{Dota 2}.
+We believe that our approach should be applicable to another MOBA games, which is share many similar key game mechanics.
+With 89.37\% in Random forest for 10 fold cross validation and 88.54\% for our independent test result shows that it is still promising and reasonable result.
+Applying Feature normalization on our classification has proved that Linear scaling with 89.77\%, but sadly, this accuracy result is not really enhanced significantly.
+Reducing our full classes was very successful with an accuracy of 94.52\% on Random forest, which is already suitable for many applications.
+Again, Random forest proved to be very stable and well suited to this domain.
+In the future we plan to look more closely at the mentioned problem of identifying the game phase and transitions more reliably.
+It might also be beneficial to detect roles not for a whole match but rather for phases or sections to account for role changes during the game.
